\chapter{Game Designer Implications}
\label{chap:results}

 The work of game designers nowadays is totally dependent by player metrics. Measuring how players react to a specific game content is a key resource for them and what is even more important is the capability of understanding the metrics in order to take the right decisions. For this reason, the activities conducted within a game company have drastically changed and as for the players, also for companies and game designers various ethical considerations must be addressed.

\section{Game Content Generation}

Years ago, when most of the games where P2P, game companies and game designers had to convince the user to buy the game, but once this was done their contribution was almost finished. Nowadays, game designers need to continuously release new content trying to retain users and to monetize as long as they can. It's extremely important that the quality of the game and the continuously generated content matches the expectations of the players. The role of a game designer is not only to develop a game but to measure, improve, adjust and change it in an infinite loop.
The time constraints and the necessity to continuously create new and high quality content puts more pressure on game designers. Some video games survive for many years and players, every day, ask for new content e.g. features, mechanisms, characters, etc. An advantage of this new business model is that game designer can test new content on a subset of players before releasing it with the risk of affecting only few of them if the generated content was not appropriate. 

Finally, the necessity of continuously developing new content has created a new field of research and applications called  Procedural Content Generation (PCG). PCG allows to create an almost infinite amount of game content. Borderlans (2K Games 2009) is an example of a game that make substantial use of PCG and it can automatically generate more than a million of weapons and equipment. No Man's Sky, an adventure survival game (Hello Games 2016) procedually generates an open universe including 18 quintillion planets. 


\section{Player Profiling and Personal Data}

In-app purchases change the way a game is created and its core mechanisms. Instead of making something that is simply fun to play, some games are designed with the specific intent of creating in the player the willingness to spend. Angry Birds GO (Rovio 2013) is only an example of such type of games. They are specifically designed to create a desired frustration-curve in its players. The goal is to annoy the players, not too much to prevent a player from quitting but enough to convince him to spend money. Their perfect player is not a pure entertained player but a more frustrated and determined one. Furthermore, modern game companies use player modeling and player profiling to target game content, special offers or ads. As an example, player modeling can be used to change the way offers and content is presented in the virtual marketplace or helping game designers to creates content that a player is more likely to buy. While player modeling refers to the use of behaviour data describing the interaction of a player with the game, player profiling use only static data e.g. gender, age or country, to segment the user base and target it. Today, game companies are significantly investing into Artificial Intelligence (AI). Last month it was the EA's turn to jump into he AI field trying to develop agents that can play the game Battlefield 1 \cite{vincent_ea_2018} and before them Ubisoft invested into a new internal AI research unit it calls “La Forge” \cite{_ubisoft_2017}. The objective is to use data and computational power to improve customization, personalization and player profiling with the goal of providing to each customer a different content based on his preferences and behaviour.
More importantly, a significant sector of this new era will be games that psychologically profile us, similarly to what Netflix does. Netflix knows what you're watching, which movies you like, when you watch them, how long you watch for, etc. The core measure for Netflix is retention. With data analysis, recommender systems and complex algorithms it tries to provide each customer with the most suitable content in order to convince him to continue to pay the monthly subscription. Similarly, game companies are going in the same direction.

Moreover, since player profiling is not game specific, it is not necessary that data are collected through the game but they can also be collected in different forms, e.g. through FB identification or Google searches and can also be combined between different games. Of course all this information can be used by game companies to improve player experience or fun and not only for monetization, but the low transparency with which companies use personal data leave several doubts.
Game companies nowadays make substantial use of personal data and this creates various ethical issue. Issues concerns: how data are collected? does the player know which data are collected? how data are used?. After years of debate the EU parliament on April 2014 approved the General Data Protection Regulation (GDPR). The goal is to harmonize data privacy laws across different European countries and to protect EU citizens' privacy. This is important because the enormous amount of data that companies are collecting nowadays could be maliciously utilized and often the involved people are not even aware of it. As a consequence, a more strict regulation and a more transparent collection of personal data it's necessary.

% \section{Private Developers}
% Finally, the last consideration regards private developers. With a F2P business model a private developer has low chances of developing his own game and it becomes more convenient to work for a publisher. The main problem is that F2P games requires investment and money are generated only in a second moment. Thanks to marketing and customer fidelity, publisher can make cheap new versions of well-known popular games discouraging private developers to create new and different games.





